Details matter: Similar host galaxies can harbor different merging compact binary populations

### 2016-07-11 paper/paper.tex
jillian edits, conclusion

\affiliation{Department of Physics and Astronomy, Vanderbilt University, Nashville TN 37235}
\email{jillian.bellovary@vanderbilt.edu}

@@

@@

\begin{acknowledgements}
ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee.
%
JB acknolwedges support  from \editremark{writeme}
\end{acknowledgements}

>>>>

\affiliation{Department of Physics, Queensborough Community College, Bayside, NY 11364}
\email{jbellovary@qcc.cuny.edu}

@@

We present a model for binary black hole \jillianremark {and other binary compact object formation?} based on models of binary formation and properties over cosmic time.  We fold these models with star formation histories and metallicity distributions taken from state of the art cosmological simulations of Milky Way-like galaxies.  We demonstrate that galaxies which appear similar at $z = 0$ but have differing merger histories will have different rates of BBH mergers detectable by LIGO.  \jillianremark{sentence detailing the specifics of this prediction, once we know what it is.}

One result of our conclusions is that we can learn about the past assembly history of a galaxy from its LIGO event rate, \jillianremark{ that's really cool.  }  Also we can use resolved star formation histories of nearby galaxies {\bf (citations)} to predict likelihoods for LIGO events.  \jillianremark { what else}\\

@@

\begin{acknowledgements}
ROS acknowledges support from NSF award AST-1412449, via subcontract from the University of Wisconsin-Milwaukee.
%
JB acknowledges generous support  from the Helen Gurley Brown Trust.
\end{acknowledgements}
